One Amazon Problem? Problem-constructions and Transnationalism in Brazilian Presidential Discourse since 1985

### 2023-02-16 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
footnote correction

While we identified the effects of setting and urgency on problem-constructions (models 2-5), the developments of problem-constructions in time also reveal unique trends. Figure 3, below, illustrates the annual share of pure-types problem-constructions since 1985. Interestingly, peak years identified in Figure 2 (above) do not coincide with increases of specific problem-constructions in Figure 3 ^[4].

^[4]: We also run lag analysis to uncover hidden patterns and identify seasonality in our data. Autocorrelation and partial autocorrelation plots for the proportion of problem-constructions in time are displayed in the appendix. The plots illustrate no significant autocorrelations between peak years and problem-constructions.

>>>>

While we identified the effects of setting and urgency on problem-constructions (models 2-5), the developments of problem-constructions in time also reveal unique trends. Figure 3, below, illustrates the annual share of pure-types problem-constructions since 1985. Interestingly, peak years identified in Figure 2 (above) do not coincide with increases of specific problem-constructions in Figure 3 [^4].

[^4]: We also run lag analysis to uncover hidden patterns and identify seasonality in our data. Autocorrelation and partial autocorrelation plots for the proportion of problem-constructions in time are displayed in the appendix.The plots illustrate no significant autocorrelations between peak years and problem-constructions.
